---
---
---

#Lets import the necessary libraries

```{r}
library(arules)
library(arulesViz)
library(tidyverse)
library(ggplot2)
library(corrplot)
library(plyr)
library(RColorBrewer)
library(plotly)
```

#Lets import the data

```{r}
data <- read.csv("/home/owekitiibwa/Desktop/dataAnalysis/Pandas-Data-Science-Tasks/all_data.csv")
```

#Data Cleaning

```{r}
#Checking for missing values
any(is.na(data))


```

Get the count of missing values in each column

```{r}
missing_counts <- colSums(is.na(data))
missing_counts
```

deleting all null values

```{r}
data <- na.omit(data)
```

Checking for duplicate values

```{r}
any(duplicated(data))
```

Removing duplicate data using the unique function

```{r}
data <- unique(data)
```

#Performing Exploratory data Analysis

Structure of the data

```{r}
str(data)
```

Descriptive Statistics of the data

```{r}
summary(data)
```

Converting columns to numeric columns

```{r}
data$Price.Each <- as.numeric(data$Price.Each)
data$Quantity.Ordered <- as.integer(data$Quantity.Ordered)
```

Drawing histograms for the numeric variables in the dataset

```{r}
  ggplot(data,aes(x= Price.Each  )) +
  geom_histogram(binwidth = 30) 
```

```{r}
ggplot(data,aes(x= Quantity.Ordered  )) +
    geom_histogram(binwidth = 0.5)
```

Drawing the density plots for the numeric variables, First for Price.Each

```{r}
ggplot(data,aes(x= Price.Each  )) + geom_density() 
```

Density Plot for Quantity Ordered

```{r}

  ggplot(data,aes(x= Quantity.Ordered  )) + geom_density()  
```

```{}
```

Data Preparation for Market Basket Analysis

```{r}
transactionData <- ddply(data,c("Order.ID","Order.Date"),
                         function(df1)paste(df1$Product,
                                            collapse = ","))
```

Viewing the transaction data

```{r}
head(transactionData)
```

This format for transaction data is called the basket format. Next, you have to store this transaction data into a .csv (Comma Separated Values) file. For this, write.csv()

```{r}
write.csv(transactionData,"/home/owekitiibwa/Desktop/dataAnalysis/Pandas-Data-Science-Tasks/transaction_data.csv", quote = FALSE, row.names = FALSE)
```

loading this transaction data into an object of the transaction class using read.transactions

```{r}
transactions <- read.transactions("/home/owekitiibwa/Desktop/dataAnalysis/Pandas-Data-Science-Tasks/transaction_data.csv", format = 'basket', sep=',')
```

Viewing the transaction object

```{r}
transactions
```

Summary of the transactions

```{r}
summary(transactions)
```

Drawing an Absolute Item Frequency Plot

```{r}
itemFrequencyPlot(transactions,topN=21,type="absolute",col=brewer.pal(8,'Pastel2'), main=" Absolute Product Frequency Plot")
```

Drawing an Relative Frequency Plot

```{r}
itemFrequencyPlot(transactions,topN=21,type="relative",col=brewer.pal(8,'Pastel2'), main=" Relative Product Frequency Plot")
```

#Generating Rules! Next step is to mine the rules using the APRIORI algorithm. The function apriori() is from package arules.

```{r}
association_rules <- apriori(transactions, parameter = list(supp=0.0001, conf=0.4,maxlen=10))
```

#Inspecting the rules Lets print number of rules

```{r}

print(association_rules)
```

Displaying the rules

```{r}
inspect(association_rules)
```

#Lets Visualize the Rules

```{r}
plot(association_rules)
```

Lets create a two key plot

```{r}
plot(association_rules,method="two-key plot")
```

Graph-Based Visualizations for association rules

```{r}
top10subRules <- head(association_rules, by = "confidence")
plot(top10subRules, method = "graph",  engine = "htmlwidget")
```
